
\input{macros}

\begin{document}


\title{Search for $WW$ and $WZ$ Resonances in $\ell\nu \MakeLowercase{qq}$ final states in $\MakeLowercase{pp}$ collisions at $\sqrt{\MakeLowercase{s}}=13$ TeV with the ATLAS detector}
\author{Natasha Woods}
\degreeyear{2019}
\degreemonth{December}
\degree{DOCTOR OF PHILOSOPHY}
\chair{Abraham Seiden}
\committeememberone{Mike Hance}
\committeemembertwo{Bruce Schumm}
\numberofmembers{3}
\deanlineone{Quentin Williams}
\deanlinetwo{Vice Provost and Dean of Graduate Studies}
\deanlinethree{}
\field{Physics}
\campus{Santa Cruz}

\begin{frontmatter}
\maketitle

\copyrightpage

\tableofcontents


\listoffigures

\listoftables
\begin{abstract}
\input{abstract}
\end{abstract}

\begin{dedication}
\vspace*{\fill}
\begin{center}
For My Parents
\end{center}
\vspace*{\fill}
\end{dedication}
\begin{acknowledgements}
Across the years, numerous connections have shaped my path, leading me to this point. Unfortunately, I cannot possibly thank everyone, and here for brevity will acknowledge a few.

Thank you Mike for being so available and supportive. Your optimism and guidance were critical to my progress. I have learned so much from our interactions and will miss them. More broadly I wish to thank past advisers, teachers, post-docs, fellow graduate students, and friends for their kindness and support. Thank you Gerard and Randi for your calm wise words and care. Thank you Adam, Ryan, and John for challenging my beliefs. 

Thank you Renae, McKenna and Caitlin for being amazing friends. Thank you Mom, Dad, Alex, Bryce and Marco for your continuous love and encouragement. 
\end{acknowledgements}

\end{frontmatter}
\part{Introduction}
\include{Introduction}

\part{Theoretical Motivation}
\include{theory}

\part {Experimental Setup}
\include{detector}
%\chapter{LHC and ATLAS Detector}
%\input{detector}

\part{The Search for $WW$ and $WZ$ Resonances in $\ell\nu qq$ final states}
\input{analysis}
\input{results}

\part{Quark and Gluon Tagging}
\input{quarkgluontagging}

\part{Conclusion}
\input{conclusion}

% \appendix % Uncomment if you have appendices. Add them below this exactly as you would a regular chapter.

\nocite{*}
\bibliographystyle{plain}
\singlespacing
\bibliography{dissertation}
\doublespacing

\end{document}
